Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-08-19 sections/4gluing_alt.tex
Minor changes.
..

\section{Collar-gluings and Factorization Algebras}\label{ch:gluing_disk_alg}

Given a stratified manifold $M$, and a $\otimes$-presentable $\infty$-category $\catC$, we defined the $\infty$-category $\lcfa_M (\catC)$ of locally constant factorization algebras on $M$ valued in $\catC$. We also noticed, in \Cref{thm:disk_alg=lcfa}, that factorization homology is involved in constructing these algebras from local data. This prompts us to ask if we can say something about the behavior of this $\infty$-category under collar-gluings in the manifold variable. In this section we will prove that such a result exists in both the cases of locally constant and ordinary factorization algebras.

@@

\begin{lemma}\label{lem:fbar_func}
    A collar-gluing $f:M \xrightarrow{} [-1,1]$ of a stratified manifold $M$ induces a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
    \end{equation}
    %
    which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_- \xhookrightarrow{} M, N_0 \times \mathbb{R} \xhookrightarrow{} M, N_+ \xhookrightarrow{} M)$. Moreover, this functor is even a map of $\infty$-operads.
\end{lemma}

@@

    A collar-gluing of $M$ restricts to a collar-gluing of any $N$ that has an embedding into $M$ like the objects of our category. On the right-hand side, at the level of objects, the associative algebra structure is provided by embeddings that differ in the $\mathbb{R}$ factor and the module maps are provided by embeddings of the middle $N_0 \times \mathbb{R}$ into $N_-$ and $N_+$. At the level of morphisms we send the morphism $e: N \xhookrightarrow{} N'$ to
    %
    \begin{equation}
        (e_-: N_- \xhookrightarrow{} N'_-, \ e_0: N_0 \times \mathbb{R} \xhookrightarrow{} N'_0 \times \mathbb{R}, \ e_+: N_+ \xhookrightarrow{} N'_+).
    \end{equation}
    %
    The existence of these maps can be stated as the existence of a unique factorization, as in e.g.
    %
    \begin{equation}\label{cd:factorization_of_e}
        \begin{tikzcd}
            N_- \arrow[r, hook] \arrow[rd, dashed, hook, "e_-"'] & N \arrow[r, hook, "e"] & N', \\
            & N'_- \arrow[ru, hook] &
        \end{tikzcd}
    \end{equation}
    %
    where the diagram commutes on the nose. Such an assignment clearly plays well with the algebra structure of the right-hand side, through the existence of (on the nose) commutative diagrams like e.g.
    %
    \begin{equation}
        \begin{tikzcd}
            N_0 \times \mathbb{R} \arrow[r, hook, "e_0"] \arrow[d, hook] & N'_0 \times \mathbb{R} \arrow[d, hook]\\
            N_- \arrow[r, hook, "e_-"] & N'_-,
            \end{tikzcd}
    \end{equation}
    %
    so that we clearly get a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}).
    \end{equation}
    %
    That the functor is a map of $\infty$-operads is clear from the fact that the key role on both sides is played by disjoint union. 
\end{proof}

@@

    Generically though, these pieces will not be disks again, so we can't simply inherit the local constancy property immediately. To alleviate this issue we make use of \Cref{thm:decom_strat_man} which assures us that every manifold can be obtained by collar-gluings and sequential colimits if we start with disks. In fact, since our largest manifold of interest is a disk, which is finitary, we only need collar-gluings, and not sequential colimits. Thus, we can work inductively and iterate the cutting and gluing process until the pieces become disks. The only thing that we need to check is that through one inductive step the equivalences remain compatible.

    Specifically, by compatibility here we mean that there is a commutative diagram
    %
    \begin{equation}\label{cd:equivs_from_lc}
        \begin{tikzcd}
            \int_{U_-} A_- \arrow[d, "\simeq"] & \int_{U_0 \times \mathbb{R}} A_0 \arrow[d, "\simeq"] \arrow[l] \arrow[r] & \int_{U_+} A_+ \arrow[d, "\simeq"] \\
            \int_{V_-} A_- & \int_{V_0 \times \mathbb{R}} A_0 \arrow[l] \arrow[r] & \int_{V_+} A_+,
        \end{tikzcd}
    \end{equation}
    %
    where the horizontal arrows are induced by the relevant embeddings. A sufficient condition to guarantee compatibility is that all collar-gluings are defined as collar-gluings of $M$ and then inherited to every open submanifold through its embedding in $M$. Focusing on the final two consecutive collar-gluings we get a commutative diagram, which we schematically denote
    %
    \begin{equation}
        \begin{tikzcd}
            -+ & 0+ \arrow[l] \arrow[r] & ++\\
            -0 \arrow[u] \arrow[d] & 00 \arrow[u] \arrow[l] \arrow[r] \arrow[d] & +0 \arrow[d] \arrow[u] \\
            -- & 0- \arrow[l] \arrow[r] & +-,
        \end{tikzcd}
    \end{equation}
    %
    one for each of $U$ and $V$. Stacking these two with the equivalence as connecting arrows is again a commutative diagram. This is enough information to guarantee that after acting with the bar construction in one direction we again get compatible equivalences. The key point being that we consider the collar-gluings on all pieces in both orders to get all the necessary arrows.

    \begin{multicols}{2}
        \begin{figure}[H]
            \centering
            \includegraphics[width=5cm]{../images/extend_gluing.png}
            \caption{Extending a collar-gluing.}
            \label{fig:extend_gluing}
        \end{figure}
        %
        The final point to check is that we have not limited ourselves by insisting to only consider collar-gluings which are inherited from ones on $M$. This is best shown in \Cref{fig:extend_gluing}. Namely, given the disk $V \xhookrightarrow{} M$, we can take a larger disk $V'$, which is guaranteed to exist from the fact that $M$ is a manifold. The figure then shows that given any collar-gluing of $V$ how we can find one particular collar-gluing of $M$ that extends the one of $V$. Since $V'$ is a disk, the figure does not obscure any detail.
    \end{multicols}
\end{proof}

@@

We know from \Cref{thm:decom_strat_man} that any manifold can be constructed from basics by iterated collar-gluings and sequential colimits. Having described what happens to a locally constant factorization algebras under collar-gluings of manifolds, we now turn to sequential colimits. {\color{red} The gluing result has an ordinary (nonhomotopy) limit. Is this also the output of the (co)bar construction?}

>>>>

\section{Collar--gluings and Factorization Algebras}\label{ch:gluing_disk_alg}

Given a stratified manifold $M$, and a $\otimes$-presentable $\infty$-category $\catC$, we defined the $\infty$-category $\lcfa_M (\catC)$ of locally constant factorization algebras on $M$ valued in $\catC$. We also noticed, in \Cref{thm:disk_alg=lcfa}, that factorization homology is involved in constructing these algebras from local data. This prompts us to ask if we can say something about the behavior of this $\infty$-category under collar--gluings in the manifold variable. In this section we will prove that such a result exists in both the cases of locally constant and ordinary factorization algebras.

@@

\begin{lemma}\label{lem:fbar_func}
    A collar-gluing $f:M \xrightarrow{} [-1,1]$ of a stratified manifold $M$ induces a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
    \end{equation}
    %
    which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_- \xhookrightarrow{} M, N_0 \times \mathbb{R} \xhookrightarrow{} M, N_+ \xhookrightarrow{} M)$.
\end{lemma}

@@

    A collar-gluing of $M$ restricts to a collar-gluing of any $N$ that has an embedding into $M$ like the objects of our category. On the right-hand side, at the level of objects, the associative algebra structure is provided by embeddings that differ in the $\mathbb{R}$ factor and the module maps are provided by embeddings of the middle $N_0 \times \mathbb{R}$ into $N_-$ and $N_+$. At the level of morphisms we send the morphism $e: N \xhookrightarrow{} N'$ to
    %
    \begin{equation}
        (e_-: N_- \xhookrightarrow{} N'_-, \ e_0: N_0 \times \mathbb{R} \xhookrightarrow{} N'_0 \times \mathbb{R}, \ e_+: N_+ \xhookrightarrow{} N'_+).
    \end{equation}
    %
    The existence of these maps can be stated as the existence of a unique factorization, as in e.g.
    %
    \begin{equation}\label{cd:factorization_of_e}
        \begin{tikzcd}
            N_- \arrow[r, hook] \arrow[rd, dashed, hook, "e_-"'] & N \arrow[r, hook, "e"] & N', \\
            & N'_- \arrow[ru, hook] &
        \end{tikzcd}
    \end{equation}
    %
    where the diagram commutes on the nose. Such an assignment clearly plays well with the algebra structure of the right-hand side, through the existence of (on the nose) commutative diagrams like e.g.
    %
    \begin{equation}
        \begin{tikzcd}
            N_0 \times \mathbb{R} \arrow[r, hook, "e_0"] \arrow[d, hook] & N'_0 \times \mathbb{R} \arrow[d, hook]\\
            N_- \arrow[r, hook, "e_-"] & N'_-,
            \end{tikzcd}
    \end{equation}
    %
    so that we clearly get a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}).
    \end{equation}
\end{proof}

@@

    Generically though, these pieces will not be disks again, so we can't simply inherit the local constancy property immediately. To alleviate this issue we make use of \Cref{thm:decom_strat_man} which assures us that every manifold can be obtained by collar--gluings and sequential colimits if we start with disks. In fact, since our largest manifold of interest is a disk, which is finitary, we only need collar--gluings, and not sequential colimits. Thus, we can work inductively and iterate the cutting and gluing process until the pieces become disks. The only thing that we need to check is that through one inductive step the equivalences remain compatible.

    Specifically, by compatibility here we mean that there is a commutative diagram
    %
    \begin{equation}\label{cd:equivs_from_lc}
        \begin{tikzcd}
            \int_{U_-} A_- \arrow[d, "\simeq"] & \int_{U_0 \times \mathbb{R}} A_0 \arrow[d, "\simeq"] \arrow[l] \arrow[r] & \int_{U_+} A_+ \arrow[d, "\simeq"] \\
            \int_{V_-} A_- & \int_{V_0 \times \mathbb{R}} A_0 \arrow[l] \arrow[r] & \int_{V_+} A_+,
        \end{tikzcd}
    \end{equation}
    %
    where the horizontal arrows are induced by the relevant embeddings. A sufficient condition to guarantee compatibility is that all collar--gluings are defined as collar--gluings of $M$ and then inherited to every open submanifold through its embedding in $M$. Focusing on the final two consecutive collar--gluings we get a commutative diagram, which we schematically denote
    %
    \begin{equation}
        \begin{tikzcd}
            -+ & 0+ \arrow[l] \arrow[r] & ++\\
            -0 \arrow[u] \arrow[d] & 00 \arrow[u] \arrow[l] \arrow[r] \arrow[d] & +0 \arrow[d] \arrow[u] \\
            -- & 0- \arrow[l] \arrow[r] & +-,
        \end{tikzcd}
    \end{equation}
    %
    one for each of $U$ and $V$. Stacking these two with the equivalence as connecting arrows is again a commutative diagram. This is enough information to guarantee that after acting with the bar construction in one direction we again get compatible equivalences. The key point being that we consider the collar--gluings on all pieces in both orders to get all the necessary arrows.

    \begin{multicols}{2}
        \begin{figure}[H]
            \centering
            \includegraphics[width=5cm]{../images/extend_gluing.png}
            \caption{Extending a collar-gluing.}
            \label{fig:extend_gluing}
        \end{figure}
        %
        The final point to check is that we have not limited ourselves by insisting to only consider collar--gluings which are inherited from ones on $M$. This is best shown in \Cref{fig:extend_gluing}. Namely, given the disk $V \xhookrightarrow{} M$, we can take a larger disk $V'$, which is guaranteed to exist from the fact that $M$ is a manifold. The figure then shows that given any collar-gluing of $V$ how we can find one particular collar-gluing of $M$ that extends the one of $V$. Since $V'$ is a disk, the figure does not obscure any detail.
    \end{multicols}
\end{proof}

@@

We know from \Cref{thm:decom_strat_man} that any manifold can be constructed from basics by iterated collar--gluings and sequential colimits. Having described what happens to a locally constant factorization algebras under collar--gluings of manifolds, we now turn to sequential colimits. {\color{red} The gluing result has an ordinary (nonhomotopy) limit. Is this also the output of the (co)bar construction?}
